---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# archnetan

<!-- badges: start -->
[![R-CMD-check](https://github.com/nesaking100/archnetan/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/nesaking100/archnetan/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of archnetan is to make network analysis of archaeological artifacts easier!
It provides functions to analyse the similarity between different artifact 'features'
and detect network communities between them.

## Installation

You can install the development version of archnetan from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("nesaking100/archnetan")
```

## Example

This is a basic example of how to generate an example network (using data from 
Ahuahu Great Mercury Island in New Zealand):

```{r example}
library(archnetan)
## basic example code
```
